Illusion Game Validation (Study 1)

### 2022-08-03 study1.Rmd
update figs

  # Assign color from the same palette to every observation of data (for geom_dots)
  data$color <- colors[as.character(diffvals[max.col(-abs(outer(data$Illusion_Difference, diffvals, "-")))])]

@@

  pred |>
    ggplot(aes(x = Illusion_Strength, y = Predicted)) +
    geom_dots(
      data = mutate(data, 
                    Illusion_Strength = round(Illusion_Strength, 1)),
      aes(x=x, y = Error, group = Error, side = .dots_side), 
      fill = data$color,
      color = NA, 
      alpha=0.5) +
    geom_slab(data=data, aes(y = Error)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Illusion_Difference, group = Illusion_Difference), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.05, 0.5, 0.95), linetype = "dotted", alpha = 0.5) +
    geom_line(aes(color = Illusion_Difference, group = Illusion_Difference)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    coord_cartesian(xlim=c(min(data$Illusion_Strength), max(data$Illusion_Strength))) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

@@

```{r message=FALSE, warning=FALSE, cache=cache}
std_params <- function(model, min=0, max=1) {
  estimate_relation(
  model,
    at = list(Illusion_Strength = c(0), 
              Illusion_Difference = seq(min, max, length.out=500)),
    ) |> 
    select(Illusion_Strength, Illusion_Difference, Error = Predicted) |> 
    slice(c(which.min(abs(Error - 0.005)), 
            which.min(abs(Error - 0.025)), 
            which.min(abs(Error - 0.25)))) |> 
    mutate(Error = insight::format_value(Error, as_percent=TRUE))
}

@@

std_params(model)
std_params(gam$model)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)
unique(data$Illusion_Strength)

@@

```{r message=FALSE, warning=FALSE, cache=cache}
range(data$Illusion_Difference)
range(data$Illusion_Strength)

>>>>

  # Assign color from the same palette to every observation of data (for geom_dots)
  closest <- diffvals[max.col(-abs(outer(data$Illusion_Difference, diffvals, "-")))]
  data$color <- colors[as.character(closest)]
  data$color <- fct_reorder(data$color, closest)

@@

  pred |>
    ggplot(aes(x = Illusion_Strength, y = Predicted)) +
    geom_dots(
      data = mutate(data, 
                    Illusion_Strength = round(Illusion_Strength, 1)),
      aes(x=x, y = Error, group = Error, side = .dots_side, order=color), 
      fill = data$color,
      color = NA, 
      alpha=0.5) +
    geom_slab(data=data, aes(y = Error)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Illusion_Difference, group = Illusion_Difference), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.05, 0.5, 0.95), linetype = "dotted", alpha = 0.5) +
    geom_line(aes(color = Illusion_Difference, group = Illusion_Difference)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_manual(values = colors) +
    scale_fill_manual(values = colors) +
    coord_cartesian(xlim=c(min(data$Illusion_Strength), max(data$Illusion_Strength))) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

@@

```{r message=FALSE, warning=FALSE, cache=cache}
std_params <- function(model, min=0, max=2) {
  estimate_relation(
  model,
    at = list(Illusion_Strength = c(0), 
              Illusion_Difference = seq(min, max, length.out=500)),
    ) |> 
    select(Illusion_Strength, Illusion_Difference, Error = Predicted) |> 
    slice(c(which.min(abs(Error - 0.005)), 
            which.min(abs(Error - 0.025)), 
            which.min(abs(Error - 0.25)))) |> 
    mutate(Error = insight::format_value(Error, as_percent=TRUE))
}

@@

std_params(model, min=0, max=2)
std_params(gam$model, min=0, max=2)
```

@@

@@
